### 2013-05-17 inst/examples/policycosts/writeup.Rmd
Working out the Apples-to-Apples case based on total costs, #35

``` {r libraries, include=FALSE}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

@@

@@

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

@@

@@

@@

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This containst the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

Quadratic costs on fishing effort have to be done separately,

>>>>

@@

Define the parameters of our cost function. We will 
consider a fixed price and fixed $c_0$ cost per unit effort.  
An additional "policy cost" is introduced through the $c_2$
coefficient, which can take a range of values. We will loop
over this range for each of the functional forms of the policy
cost, in order to choose coefficients $c_2$ in each case
that are comparable.

@@

Clean the workspace and load the required libraries.

``` {r libraries}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

This block defines the various parameters 
and nuisance parameters we need to specify our
optimal control problem.

@@

Given these parameters, we can determine the optimal solution under the classic assumption of "adjustment-free" costs, where there is no penalty for adjusting the value of the control (harvest) at each decision step (year).

@@

Now we introduce the functional forms for each of the adjustment costs,

@@

Before we can start comparing solutions induced
under each of these costs, we need to scale them
appropriately (e.g. the coefficient $c_2$ has 
different units and a different magnitude of 
effect when multiplied by quadratic differences
$(h_{t} - h_{t-1})^2$ then when multiplied by 
linear differences $h_{t} - h_{t-1}$.

To do so we loop over a grid of $c_2$ values and
determine the net present value under each functional 
form of adjustment costs for each $c_2$ in our grid.

@@

Note that `optim_policy` has been updated to return the equilibrium value of profits from fish harvests before the adjustment costs have been paid, `penalty_free_V`.  This contains the values for all possible states, we simply evaluate it at the carrying capacity (which is our initial condition.)  The index in `x_grid` that corresponds to the carrying capacity (initial condition) `i` indicates this.

We also do the the classical quadratic costs on fishing effort separately,
